Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
removes ._expanded_PF and ._expanded_HL

transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)

@@

AR_expanded_taken <- my_apriori(transactions_expanded)
# creating vector of fail course
course_id_fail <- d_transactions_expanded %>%
  filter(PF == "fail") %>%
  distinct(`item_PF`)

AR_expanded_PF <- my_apriori(transactions_expanded_PF,
                    appearance = list(both = course_id_fail$`item_PF`))

# creating vector of low score course
course_id_low <- d_transactions_expanded %>%
  filter(HL == "low") %>%
  distinct(`item_HL`)

AR_expanded_HL <- my_apriori(transactions_expanded_HL,
                    appearance = list(both = course_id_low$`item_HL`))

@@

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
##pass/fail filter
SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% 
  filter(`RHS Quality`=="fail")
##high/low filter
SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% 
  filter(`RHS Quality`=="low")

>>>>

transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
#transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
#transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
#sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
#sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)

@@

AR_expanded_taken <- my_apriori(transactions_expanded)
# creating vector of fail course
#course_id_fail <- d_transactions_expanded %>%filter(PF == "fail") %>%distinct(`item_PF`)
#AR_expanded_PF <- my_apriori(transactions_expanded_PF,appearance = list(both = course_id_fail$`item_PF`))

# creating vector of low score course
#course_id_low <- d_transactions_expanded %>%filter(HL == "low") %>%distinct(`item_HL`)
#AR_expanded_HL <- my_apriori(transactions_expanded_HL, appearance = list(both = course_id_low$`item_HL`))

@@

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
##pass/fail filter
#SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% filter(`RHS Quality`=="fail")
##high/low filter
#SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% filter(`RHS Quality`=="low")
